\documentclass[oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

%SetFonts

%SetFonts


\title{Heuristic Analysis}
\author{Ilya Nikokoshev}
\date{February 25, 2018}

\newcommand{\C}[1]{\texttt{C#1}}
\newcommand{\JFK}{\texttt{JFK}}
\newcommand{\SFO}{\texttt{SFO}}
\newcommand{\ATL}{\texttt{ATL}}
\newcommand{\bfs}{\texttt{breadth\_first\_search}}
\newcommand{\dfs}{\texttt{depth\_first\_graph\_search}}
\newcommand{\ucs}{\texttt{uniform\_cost\_search}}
\newcommand{\hip}{\texttt{h\_ignore\_preconditions}}
\newcommand{\hpg}{\texttt{h\_pg\_levelsum}}

\begin{document}
\maketitle

\begin{abstract}
As part of the Project 3 in the Artificial Intelligence Nanodegree Program, we implement a planning search agent to solve deterministic logistics planning problems using an example of an Air Cargo transport system.
\end{abstract}

\section{Problem Solutions}

\begin{tabular}{lll}

\textbf{Problem 1 Solution} & 
\textbf{Problem 2 Solution} &
\textbf{Problem 3 Solution} \\

\begin{minipage}{2in}
\begin{verbatim}

Load(C1, P1, SFO)
Load(C2, P2, JFK)
Fly(P1, SFO, JFK)
Unload(C1, P1, JFK)
Fly(P2, JFK, SFO)
Unload(C2, P2, SFO)






\end{verbatim}
\end{minipage}

&

\begin{minipage}{2in}
\begin{verbatim}

Load(C1, P1, SFO)
Load(C2, P2, JFK)
Load(C3, P3, ATL)
Fly(P2, JFK, SFO)
Unload(C2, P2, SFO)
Fly(P1, SFO, JFK)
Unload(C1, P1, JFK)
Fly(P3, ATL, SFO)
Unload(C3, P3, SFO)



\end{verbatim}
\end{minipage}

&

\begin{minipage}{2in}
\begin{verbatim}

Load(C2, P2, JFK)
Load(C1, P1, SFO)
Fly(P2, JFK, ORD)
Load(C4, P2, ORD)
Fly(P1, SFO, ATL)
Load(C3, P1, ATL)
Fly(P1, ATL, JFK)
Unload(C1, P1, JFK)
Unload(C3, P1, JFK)
Fly(P2, ORD, SFO)
Unload(C2, P2, SFO)
Unload(C4, P2, SFO)
\end{verbatim}
\end{minipage}

\end{tabular}

\section{Non-heuristic Searches}

We present results for the runs of three uninformed planning strategies in the Table \ref{NonHeuristic}. The selected strategies are Breadth First Search, Uniform Cost Search and Depth First Graph Search. Those strategies do not use any additional information about the structure of the problem states.

In line with the results in the Chapter 3 (all references are to the AIMA book), Breadth First Search and Uniform Cost Search always produce the optimal plan. 

Figure 3.21 in Section 3.4.7 goes into more detail regarding the time and space complexity of selected methods. In particular, Depth First Graph Search has its own advantages as it uses less memory and is practically faster in our runs. However, the solutions it finds are typically very far from 
optimal.

\begin{table}[ht]
\caption{Results for Non-heuristic planinng methods}
\begin{center}
\begin{tabular}{c|c|ccccc}
   & Search Method & Length & Optimal? & Time Elapsed & Expansions & Goal Tests \\
   \hline
1 & \bfs & 6 & Yes & 0.15 & 43 & 56 \\
1 & \dfs & 12 & No & 0.04 & 12 & 13 \\
1 & \ucs & 6 & Yes & 0.19 & 55 & 57 \\
   \hline
2 & \bfs & 9 & Yes & 45.23 & 3343 & 4609 \\
2 & \dfs & 575 & No & 10.36 & 582 & 583 \\
2 & \ucs & 9 & Yes & 69.89 & 4853 & 4855 \\
   \hline
3 & \bfs & 12 & Yes & 255.13 & 14663 & 18098 \\
3 & \dfs & 596 & No & 7.58 & 627 & 628 \\
3 & \ucs & 12 & Yes & 184.44 & 18223 & 18225    
\end{tabular}
\end{center}
\label{NonHeuristic}
\end{table}%


\section{Heuristic Searches}

We present results for the runs of an A* search with two heuristics, Ignore Preconditions (\hip) and Level Sum (\hpg), in the Table \ref{Heuristic}. 

As proven in Section 3.5.2, A* search always finds optional solution, provided that the heuristics is consistent. This is confirmed by our results.

The results show that using A* search with Level Sum heuristics requires less Node Expansions and Goal Tests to find optional solutions than any other method. However, this heuristic itself is computationally expensive and using Ignore Preconditions allows us to perform the search much faster in practice, dominating all other optimal methods.

\begin{table}[ht]
\caption{Results for Heuristic planinng methods}
\begin{center}
\begin{tabular}{c|c|ccccc}
   & Heuristic & Length & Optimal? & Time Elapsed & Expansions & Goal Tests\\
   \hline
1 & \hip & 6 & Yes & 0.10 & 41 & 43 \\
1 & \hpg & 6 & Yes & 0.69 & 11 & 13 \\
   \hline
2 & \hip & 9 & Yes & 12.85 & 1450 & 1452 \\
2 & \hpg & 9 & Yes & 67.36 &  86 & 88  \\
   \hline
3 & \hip & 12 & Yes & 59.05 & 5040 & 5042 \\
3 & \hpg & 12 & Yes & 336.54 & 325 & 327 
\end{tabular}
\end{center}
\label{Heuristic}
\end{table}%

\section{Conclusion}

We have compared five different strategies of finding a solution to the Air Cargo problem. Using informed search we were able to achieve a good balance by finding an optional solution faster using A* search with domain-independent Ignore Preconditions heuristic. 


\end{document}  